Author: Brady M. Chisholm
University of Minnesota Twin Cities
Department of Psychology

libraries to help with MATLAB 
```{r}
library(R.matlab)   # To read .mat files
library(mgcv)       # For GAMM analysis
```

Get subject ID list 
```{r}
source("")
```


within data folder subjects are named two ways
P<xx>
HI<xx>

JM's original pathnames 
#mat_dir <- ['M:\Lab_Shared\Juraj\SpeechEEG_SentencesWithPupillometry\' folderName '\' sessionType subjId '\' eyeTrack'];

Recoding values 
```{r}
setwd("M:\Lab_Shared\Juraj\SpeechEEG_SentencesWithPupillometry")
```

# Directory w/ .mat files
```{r}
mat_files <- list.files(mat_dir, pattern = "\\.mat$", full.names = TRUE)
```

# store model results in a list 
```{r}
gamm_results <- list()
```

# Loop over each subject's .mat file
```{r}
for(file in mat_files) {
  # Read .mat file
  mat_data <- readMat(file) 
  
  # Extract data
  # Uses dummy .mat variable 'data', assuming 3 columns of time, size, cond, trial 
  
  subject_df <- as.data.frame(mat_data$data)
  # recode columns?
  
  # Model pupil AU as a function of a smooth term over time, parametric effect of condition, and a smooth-by-condition interaction.
  # Random intercept for "trial"
  GMod1 <- gamm(pupil ~ s(time) + condition + s(time, by = condition),
                random = list(trial = ~1),
                data = subject_df)
  
  # Use the file with no extension as subjs id 
  subject_id <- tools::file_path_sans_ext(basename(file))
  gamm_results[[subject_id]] <- GMod1
} # if end
```

```{r}
# Review the summary of subjs model 
lapply(gamm_results, summary)
```


